Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-11 SUBMISSION_02/article/article.tex
Commit 2024-09-11 12:14

The GHI data are available as hourly values in the WMO World Radiation
Data Center (http://wrdc.mgo.rssi.ru). The relevant source code can be
found in github and is register to zenodo the preparation of GHI data
the detection of clouds the processes for this manuscript

Cloud identification \citet{thanasis_n_2024_13744460}

GHI \citet{natsis_2024_13744467}

this \citet{thanasis_n_2024_13744472}

>>>>

The GHI data are available as hourly values in the WMO World Radiation
Data Center\footnote{\url{http://wrdc.mgo.rssi.ru}}.The relevant source
code is available in three repositories for (a) the preparation of GHI
data \citep{natsis_2024_13744467} (b) the detection of clouds
\citep{thanasis_n_2024_13744460} and (c) the processes for this
manuscript \citep{thanasis_n_2024_13744472}.
